Variational Monte Carlo on bosonic systems

### 2018-03-25 project_1/article/article.tex
Scale images to avoid overfull hbox

            \begin{figure}
                \centering
                    \includegraphics[width=250px]
                    {../data/figures/problem_c1.pdf}
                    \caption{As the number of Monte Carlo cycles increases the
                    standard deviation of the local energies decrease. This
                    effect is stronger when the importance sampling scheme is
                    employed.}
                    \label{fig:problem_c1}
            \end{figure}

            \begin{figure}
                \centering
                    \includegraphics[width=250px]
                    {../data/figures/problem_c2.pdf}
                    \caption{The absolute difference between the expected energy
                    and the exact energy for both brute force and importance
                    sampling. }
                    \label{fig:problem_c2}
            \end{figure}

@@

            \begin{figure}
                \includegraphics[width=250px]{../data/figures/problem_f.pdf}
                \caption{In this figure we can see the convergence of different
                starting values for $\alpha$ towards the true value of $\alpha$
                that minimizes the expected energy in the interacting case.}
                \label{fig:gradient_descent_interacting}
            \end{figure}

@@

        \begin{figure}
            \includegraphics[width=250px]{../data/figures/problem_e.pdf}
            \caption{Local energies as a function of variational parameter $\alpha$
                             for different number of particles.}
            \label{fig:interacting}
        \end{figure}

>>>>

            \begin{figure}
                \centering
                    \includegraphics[width=244px]
                    {../data/figures/problem_c1.pdf}
                    \caption{As the number of Monte Carlo cycles increases the
                    standard deviation of the local energies decrease. This
                    effect is stronger when the importance sampling scheme is
                    employed.}
                    \label{fig:problem_c1}
            \end{figure}

            \begin{figure}
                \centering
                    \includegraphics[width=244px]
                    {../data/figures/problem_c2.pdf}
                    \caption{The absolute difference between the expected energy
                    and the exact energy for both brute force and importance
                    sampling. }
                    \label{fig:problem_c2}
            \end{figure}

@@

            \begin{figure}
                \includegraphics[width=244px]{../data/figures/problem_f.pdf}
                \caption{In this figure we can see the convergence of different
                starting values for $\alpha$ towards the true value of $\alpha$
                that minimizes the expected energy in the interacting case.}
                \label{fig:gradient_descent_interacting}
            \end{figure}

@@

        \begin{figure}
            \includegraphics[width=244px]{../data/figures/problem_e.pdf}
            \caption{Local energies as a function of variational parameter
            $\alpha$ for different number of particles.}
            \label{fig:interacting}
        \end{figure}
